---
title: 
output: 
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["tabu", "booktabs", "xcolor", "colortbl", "textcomp"]
#fontfamily: helvet
mainfont: Arial
fontsize: 11pt
params: 
  contractor: 'blank'
  client: 'blank'
  item: 'blank'
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(kableExtra)
library(lubridate)
library(fontawesome)

options(knitr.kable.NA = '')
options(scipen = 999)

name <- params[['contractor']][['name']]
date <- format(Sys.Date(), '%d.%m.%Y')
signature <- params[['contractor']][['signature']] %>% image_scale('x50')
pcode <- params[['contractor']][['address_pcode']] %>% as.character()
city <- params[['contractor']][['address_city']] %>% as.character()
```


\makebox[0.5\linewidth][l]{\large\textbf{`r name`} }\makebox[0.5\linewidth][r]{\huge\textbf{INVOICE}} \newline

`r params[['contractor']][['address_street']]` \newline
`r params[['contractor']][['address_pcode']] %>% as.character()` `r params[['contractor']][['address_city']]` \newline
`r fa("envelope", fill = "darkred")` `r params[['contractor']][['mail']] %>% as.character()` \newline
`r fa("phone-square", fill = "darkred")` `r params[['contractor']][['phone']] %>% as.character() %>% str_remove("'")`

\begin{flushright}`r date`\end{flushright} 
 
**Recipient** \newline
`r params[['client']][['name']]` \newline
`r params[['client']][['address_street']]` \newline
`r params[['client']][['address_pcode']] %>% as.character()` `r params[['client']][['address_city']]` \newline

Thank you for your order. We charge you for the following services

```{r table, echo=F, eval = T}
items <- tibble(
  item = params[['item']][['name']],
  item_desc = params[['item']][['desc']],
  hours = as.numeric(params[['item']][['days']]),
  rate = as.numeric(params[['contractor']][['salary']])
  ) %>% 
  mutate(
    id = row_number(),
    amount = round(hours * rate, 2)
    )

sums <- items %>% group_by() %>% summarize(amount = sum(amount, na.rm = T)) %>% mutate(item = 'Total')

items %>%
  select(id, item, item_desc, hours, rate, amount) %>% 
  mutate(
    rate = paste('\\texteuro  \\enspace', format(rate, digits = 2, nsmall = 1, big.mark = '.', decimal.mark = ',')),
    amount = paste('\\texteuro  \\enspace', format(amount, digits = 2, nsmall = 1, big.mark = '.', decimal.mark = ','))
  ) %>% 
  knitr::kable(format = 'latex', booktabs = T, escape = F, col.names = c('\\#', 'Item', 'Description', 'Hours', 'Rate', 'Amount'), align = c('c', 'l', 'l', 'r', 'r', 'r')) %>%
  row_spec(0, bold = T) %>% 
  column_spec(1, width = '.5cm') %>%
  column_spec(2, width = '3cm') %>%
  column_spec(3, width = '5cm') %>%
  column_spec(c(4, 5, 6), width = '2cm') %>% 
  sub("\\\\toprule", "\\\\toprule[1pt]", .) %>% 
  sub("\\\\bottomrule", "", .)
```

\renewcommand{\arraystretch}{1.5}

```{r table_sums, echo=F, eval = T}
sums <- 
  items %>% 
  group_by() %>% 
  summarize(amount = sum(amount, na.rm = T)) %>% 
  mutate(id = ' ', item = ' ', item_desc = ' ', hours = ' ', rate = 'Total')

sums %>%
  select(id, item, item_desc, hours, rate, amount) %>% 
  mutate(amount = paste('\\texteuro \\enspace', format(amount, digits = 2, nsmall = 1, big.mark = '.', decimal.mark = ','))) %>% 
  knitr::kable(format = 'latex', booktabs = T, escape = F, col.names = NULL, align = c('r', 'r', 'r', 'r', 'r', 'r'), linesep = "\\addlinespace") %>% 
  row_spec(1, bold = T, color = "white", background = "black") %>% 
  column_spec(1, width = '.5cm') %>%
  column_spec(2, width = '3cm') %>%
  column_spec(3, width = '5cm') %>%
  column_spec(c(4, 5, 6), width = '2cm') %>%
  sub("\\\\toprule", "", .) %>% 
  sub("\\\\bottomrule", "\\\\bottomrule[1pt]", .)
```

\vskip 1cm

\centering\large Thanks for your trust and good cooperation!

\centering\large Best regards to `r params[['client']][['address_street']]`

\vskip 2cm

\centerline{\raisebox{-.3cm}[.3cm][0cm]{\makebox[6cm][c]{`r date`, `r city`}}\makebox[0.5cm][c]{}\raisebox{-.9cm}[.2cm][0cm]{\makebox[6cm][c]{`r signature`}}}
\centerline{\makebox[6cm][c]{\hrulefill}\makebox[0.5cm][c]{}\makebox[6cm][c]{\hrulefill}}
\centerline{\makebox[6cm][c]{Date, Place}\makebox[0.5cm][c]{}\makebox[6cm][c]{`r name`}}
 
\hrulefill

\begin{center}\textbf{Institute} `r params[['contractor']][['bank_branch_addr']]` \textbf{IBAN} `r params[['contractor']][['ac_no']]` \textbf{BIC} `r params[['contractor']][['bic']]`\end{center}